Asymmetric relationships and their effects on coexistence

### 2023-05-15 paper/Paper.Rnw
deleted some old commented material
fixed a typo
Jasmin addressing cmments

%packages
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[left=2cm,top=2cm,right=2cm,bottom=1.5cm,head=.5cm,foot=.5cm]{geometry}
\usepackage{url}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{subfig}
\usepackage{float}
\usepackage{setspace}
\usepackage{lineno}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{xr}
\usepackage{relsize}
\usepackage{tikz}

@@

\affil[a]{Department of Ecology and Evolutionary Biology and Center for Ecological Research, University of Kansas}
\affil[b]{Environmental Studies Program and Department of Biology, Universit of Oregon}
\affil[c]{Laboratory of Populations, Rockefeller University}
\affil[*]{Corresponding author, reuman@ku.edu}

@@

The authors thank Shyamolina Ghosh for suggesting the research problem, and Lawrence Sheppard, Max Castorani,
Jon Walter, Jude Kastens, Vadim Karatayev, Emily Arsenault, Neil Thimmesch, Laurn Hallett, and 
Robin Snyder for helpful discussions. 
The authors especially thank Steve Ellner for key advice at several watershed moments in the development of the project. 
The authors were partly supported by US National
Science Foundation grants 1714195 and 2023474, the James S McDonnell Foundation, the California Department of Fish and
Wildlife Delta Science Program, and the Alexander von Humboldt Foundation.

@@

%***DAN: Jasmin, this figure looks really great. Here are a few minor things I would like to ask you to
%do to further optimize:
%1) Currently there are axis labels and numbers only on the bottom and left panels, which makes sense.
%But the axis tick marks needs to occur on all panels. I noticed that this would be an imporvement
%when I found myself wanting to see where the ATA line was between the x axis and the GWR line, but it was 
%a little hard to see where the x axis was becuase there were no tick marks. It is possible to have tick marks
%but no numbers of labels in R, and that's what we need here.
%2) The font of the x axis label, "log fecundity standard deviation, \sigma" seems slightly different from the 
%other textual labels. Can you please make it consistent? Perhaps it is not bold and the others are bold, or 
%something.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLLN.pdf}
\caption{The contribution of ATAs to species coexistence was sometimes, but not always, 
meaningfully large compared to 
other components of the MCT decomposition for the log-normal fecundities lottery model.
All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). For each panel, 
$\delta$ and $\mu_1-\mu_2$ 
are fixed at values specified in the margins, and GWR and components of the decomposition
are plotted against $\sigma$. The contribution of ATAs ($\Delta_i^{[EC]}$) sometimes, but not always, 
has magnitude comparable to other components, indicating that ATAs can contribute meaningfully
to species coexistence or failure to coexist. In some instances, the GWR line falls 
between the ATA line and the $x$ axis, indicating that, for those parameter values, ATAs 
make the difference between species
coexistence and exclusion of the weaker competitor. These instances, which are shaded, correspond to
ATA rescue or exclusion (Theory). Standard errors of plotted quantities 
were never greater than \Sexpr{round(se3,5)}, so are not displayed. This plot uses $q_{ij}=1$. An 
analogous plot (SI Fig. \ref{SI-fig:fig3_alt}) uses 
$q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$; though results differed
in detail, main conclusions were the same. \label{fig:fig3}}
\end{figure}

%***DAN: Jasmin, panel labels(a, b, c, etc.) need to be added. Please use the same format for these labels
%as you do in the other figures.
%Also please add tick marks to all axes (see comment on previous figure)
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLB.pdf}
\caption{The contribution of ATAs to species coexistence was often meaningfully large compared to 
other components of the MCT decomposition for the beta fecundities lottery model.
All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). For each panel,
$\delta$ is fixed at the value specified in the upper margin, 
and GWR and components of the decomposition
are plotted against the upper bound ratio, $\eta_2/\eta_1$. The contribution of ATAs ($\Delta_i^{[EC]}$) frequently 
has magnitude comparable to other components, indicating that ATAs can contribute meaningfully
to species coexistence or failure to coexist. In some instances, the GWR line falls 
between the ATA line and the $x$ axis, indicating that, for those parameter values, ATAs make 
the difference between species
coexistence and exclusion of the weaker competitor. These instances, which are shaded, correspond to
ATA rescue or exclusion (Theory). Standard errors of plotted quantities 
were never greater than \Sexpr{round(se4,5)}, so are not displayed. 
This plot uses $q_{ij}=1$. 
An analogous plot (SI Fig. \ref{SI-fig:fig4_alt}) uses 
$q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$; 
though results differed in detail, main conclusions were the same.
%***DAN: make sure this is indeed the case once the plot is generated.
}\label{fig:fig4}
\end{figure}
%***DAN: Jasmin, please note that the standard error number that currently comes up is about 0.27, which
%is actually really big compared to the plotted values. Is this a temporary value based on a limited set 
%of sims, and you're planing to do a larger number? If this is the actual value based on the final number 
%of sims that you plan to do, then we may have to figure out a way to plot standard errors. Let's discuss
%The same problem occurs for the accompany SI figure.

@@

% \begin{figure}
% \includegraphics[width=.38\textwidth]{../results_figs/fig6.pdf}
% \caption{The contribution of ATAs to GWR of \emph{F. crotonensis}
% in the diatom system of \cite{Descamps_2005} was often meaningfully large compared to 
% the GWR itself. The ratio $\Delta_i^{[EC]}/\text{GWR}$ is shown, larger magnitudes
% indicating greater importance of ATAs and values greater than $1$ corresponding to either
% ATA rescue or ATA exclusion (Methods). For this system and the plotted parameters, 
% $\Delta_i^{[EC]}$ was always positive, so cyan indicates exclusion of \emph{F. crotonensis} and
% magenta indicates coexistence of the two diatom species. Values greater than 1 or less than -1
% were remapped to 1 and -1, respectively, for readability.
% For the parameters we considered, GWR of the other species, \emph{C. pseudostelligera}, was always positive both including and
% excluding ATAs, so GWR for \emph{F. crotonensis} is a sufficient coexistence metric.
% Standard errors of plotted quantities were always less then \Sexpr{round(se6,5)}, so are not shown.} \label{fig:fig6}
% \end{figure}

>>>>

%packages
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[left=2cm,top=2cm,right=2cm,bottom=1.5cm,head=.5cm,foot=.5cm]{geometry}
\usepackage{url}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{subfig}
\usepackage{float}
\usepackage{setspace}ƒ
\usepackage{lineno}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{xr}
\usepackage{relsize}
\usepackage{tikz}

@@

\affil[a]{Department of Ecology and Evolutionary Biology and Center for Ecological Research, University of Kansas}
\affil[b]{Environmental Studies Program and Department of Biology, University of Oregon}
\affil[c]{Laboratory of Populations, Rockefeller University}
\affil[*]{Corresponding author, reuman@ku.edu}

@@

The authors thank Shyamolina Ghosh for suggesting the research problem, and Lawrence Sheppard, Max Castorani,
Jon Walter, Jude Kastens, Vadim Karatayev, Emily Arsenault, Jordan Rodriguez, Lauren Hallett, and 
Robin Snyder for helpful discussions. 
The authors especially thank Steve Ellner for key advice at several watershed moments in the development of the project. 
The authors were partly supported by US National
Science Foundation grants 1714195 and 2023474, the James S McDonnell Foundation, the California Department of Fish and
Wildlife Delta Science Program, and the Alexander von Humboldt Foundation.

@@

%***DAN: Jasmin, this figure looks really great. Here are a few minor things I would like to ask you to
%do to further optimize:
%1) Currently there are axis labels and numbers only on the bottom and left panels, which makes sense.
%But the axis tick marks needs to occur on all panels. I noticed that this would be an imporvement
%when I found myself wanting to see where the ATA line was between the x axis and the GWR line, but it was 
%a little hard to see where the x axis was becuase there were no tick marks. It is possible to have tick marks
%but no numbers of labels in R, and that's what we need here.
%2) The font of the x axis label, "log fecundity standard deviation, \sigma" seems slightly different from the 
%other textual labels. Can you please make it consistent? Perhaps it is not bold and the others are bold, or 
%something.
%***JASMIN: Done. Added ticks to other panels and make x label bold
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLLN.pdf}
\caption{The contribution of ATAs to species coexistence was sometimes, but not always, 
meaningfully large compared to 
other components of the MCT decomposition for the log-normal fecundities lottery model.
All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). For each panel, 
$\delta$ and $\mu_1-\mu_2$ 
are fixed at values specified in the margins, and GWR and components of the decomposition
are plotted against $\sigma$. The contribution of ATAs ($\Delta_i^{[EC]}$) sometimes, but not always, 
has magnitude comparable to other components, indicating that ATAs can contribute meaningfully
to species coexistence or failure to coexist. In some instances, the GWR line falls 
between the ATA line and the $x$ axis, indicating that, for those parameter values, ATAs 
make the difference between species
coexistence and exclusion of the weaker competitor. These instances, which are shaded, correspond to
ATA rescue or exclusion (Theory). Standard errors of plotted quantities 
were never greater than \Sexpr{round(se3,5)}, so are not displayed. This plot uses $q_{ij}=1$. An 
analogous plot (SI Fig. \ref{SI-fig:fig3_alt}) uses 
$q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$; though results differed
in detail, main conclusions were the same. \label{fig:fig3}}
\end{figure}

%***DAN: Jasmin, panel labels(a, b, c, etc.) need to be added. Please use the same format for these labels
%as you do in the other figures.
%Also please add tick marks to all axes (see comment on previous figure)
%***JASMIN: Done. Labels and ticks.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLB.pdf}
\caption{The contribution of ATAs to species coexistence was often meaningfully large compared to 
other components of the MCT decomposition for the beta fecundities lottery model.
All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). For each panel,
$\delta$ is fixed at the value specified in the upper margin, 
and GWR and components of the decomposition
are plotted against the upper bound ratio, $\eta_2/\eta_1$. The contribution of ATAs ($\Delta_i^{[EC]}$) frequently 
has magnitude comparable to other components, indicating that ATAs can contribute meaningfully
to species coexistence or failure to coexist. In some instances, the GWR line falls 
between the ATA line and the $x$ axis, indicating that, for those parameter values, ATAs make 
the difference between species
coexistence and exclusion of the weaker competitor. These instances, which are shaded, correspond to
ATA rescue or exclusion (Theory). Standard errors of plotted quantities 
were never greater than \Sexpr{round(se4,5)}, so are not displayed. 
This plot uses $q_{ij}=1$. 
An analogous plot (SI Fig. \ref{SI-fig:fig4_alt}) uses 
$q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$; 
though results differed in detail, main conclusions were the same.
%***DAN: make sure this is indeed the case once the plot is generated.
}\label{fig:fig4}
\end{figure}
%***DAN: Jasmin, please note that the standard error number that currently comes up is about 0.27, which
%is actually really big compared to the plotted values. Is this a temporary value based on a limited set 
%of sims, and you're planing to do a larger number? If this is the actual value based on the final number 
%of sims that you plan to do, then we may have to figure out a way to plot standard errors. Let's discuss
%The same problem occurs for the accompany SI figure.

@@
